DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-04 paper/evaluation.tex
eval summary

Figure~\ref{fig:perf-vs-corecnt} shows the average execution times of
the control loop as we vary the number of cores used by the
Tensorflow. As expected as we assign more cores, the average execution
time decreases---from 61.96 ms on a single core to 42.67 ms on four
cores. However, the improvement is far from being ideal as we expected
linear scaling. In particular, from 2 cores to 3 cores, the
improvement is mere 2.38ms (or 4\%). In short, we find that the
scalability of DeepPicar's deep neural network is not ideal on the
platform. We do not know whether it is due to the limitations of
Tensorflow's multicore implementation or it's the model's inherent
characteristics.

@@

\subsection{Summary}
We found that the DeepPicar is capable of successfully completing all
necessary inferencing operations within a given deadline of 50
ms. Between these operations, it was discovered that the angle
prediction time of the model was the dominating step in the processing
time of a single frame. The other operations were found to execute in
very little time, with either one taking 5 ms at most. When running a
single model, DeepPicar performed the best when it used all 4 cpu
cores, as it was able to process a frame in 43 ms on average. This
feat can still be accomplished when running a single model on 3 cpu
cores, and is also possible when using 2 cores. The only time in which
the Pi can't run a single model under 50 ms is when only 1 core is
used. This was also the case when multiple models were run
concurrently as no models were able to consistently complete inference
operations in under 50 ms. 
However, the DeepPicar was shown to be capable of handling other
potential WCETs. If given a larger deadline, the capabilities of
DeepPicar as an autonomous vehicle platform would be greatly
increased. For example, if tested with a deadline of 66.67 ms, or 15
fps, the platform would have passed several of the experiments
performed. In actuality, the DeepPicar would have only been
unsatisfactory in the 4 model test where it would have missed the
deadlines by $\sim$10 ms, and the benchmark tests, where  
it would still miss by $\sim$33 ms at best.

>>>>

Figure~\ref{fig:perf-vs-corecnt} shows the average execution times of
the control loop as we vary the number of cores used by the
Tensorflow. As expected as we assign more cores, the average execution
time decreases---from 61.96 ms on a single core to 42.67 ms on four
cores (a 30\% improvement). However, the improvement is far from ideal
linear scaling. In particular, from 2 cores to 3 cores, the
improvement is mere 2.38ms (or 4\%). In short, we find that the
scalability of DeepPicar's deep neural network is not ideal on the
platform. We do not know whether it is due to the limitations of
Tensorflow's multicore implementation or it's the model's inherent
characteristics.

@@

\subsection{Summary}
So far, we have systematically evaluated DeepPicar's real-time
characteristics from the perspective of end-to-end deep learning based
real-time control and made several observations.

First, we find that DeepPicar's computing platform,
the Raspberry Pi 3 Model B, offers adquate computing capacity to
to perform real-time control of the RC car at 20 Hz frequency (or
50ms per control loop). Given the complexity of the DNN we use, we are
pleasantly suprised by this finding. The time breakdown has shown that
the DNN inferencing operation, perforemd by the Tensorflow library, is
dominating the execution time, which is expected.

Second, we find that the scalability of Tensorflow's DNN inference 
implementation is not ideal: We find that using all four cores are 
only about 30\% better than using just a single core.

Third, we find that consolidating multiple DNN models---on different CPU
cores---is feasible based on the following two observations: (1)
DNN performance on a single is not much worse than on multicore; (2)
multiple DNN models running simultaneously do not cause severe
interference with each other.

Lastly, we however find that consolidating memory (DRAM) intensive
applications could jeopadize DNN performance because DNN performance
appear very sensitive to memory performance; we observe up to 9.6X
slowdown in DNN performance by co-scheduling synthetic memory
bandwidth intensive applications on idle cores.

%% is capable of successfully completing all
%% necessary inferencing operations within a given deadline of 50
%% ms. Between these operations, it was discovered that the angle
%% prediction time of the model was the dominating step in the processing
%% time of a single frame. The other operations were found to execute in
%% very little time, with either one taking 5 ms at most

%% When running a
%% single model, DeepPicar performed the best when it used all 4 cpu
%% cores, as it was able to process a frame in 43 ms on average. This
%% feat can still be accomplished when running a single model on 3 cpu
%% cores, and is also possible when using 2 cores. The only time in which
%% the Pi can't run a single model under 50 ms is when only 1 core is
%% used. This was also the case when multiple models were run
%% concurrently as no models were able to consistently complete inference
%% operations in under 50 ms.

%% However, the DeepPicar was shown to be capable of handling other
%% potential WCETs. If given a larger deadline, the capabilities of
%% DeepPicar as an autonomous vehicle platform would be greatly
%% increased. For example, if tested with a deadline of 66.67 ms, or 15
%% fps, the platform would have passed several of the experiments
%% performed. In actuality, the DeepPicar would have only been
%% unsatisfactory in the 4 model test where it would have missed the
%% deadlines by $\sim$10 ms, and the benchmark tests, where  
%% it would still miss by $\sim$33 ms at best.
